Inventor Disambiguation Report

### 2022-05-23 examples/benchmark/full-report.qmd
sync

---
title: Inventor Disambiguation Report
date: today
author: PatentsView-Evaluation
toc: true
toc-location: left
format:
    html:
        theme: cosmo
        echo: false
        fig-cap-location: margin
        code-fold: true
        code-tools: true
        code-line-numbers: true
        code-block-border-left: true
        code-copy: true
        code-block-border-left: "#31BAE9"
        code-link: true
        include-in-header: header.html
        include-after-body: footer.html
execute:
  cache: true
  freeze: true
  warning: false
  message: false
jupyter: python3
---

>>>>

---
title: Inventor Disambiguation Report
date: today
author: PatentsView-Evaluation
toc: true
toc-location: left
format:
    html:
        #theme: cosmo
        echo: false
        fig-cap-location: margin
        code-fold: true
        code-tools: true
        code-line-numbers: true
        code-block-border-left: true
        code-copy: true
        code-block-border-left: "#31BAE9"
        code-link: true
        include-in-header: header.html
        include-after-body: footer.html
execute:
  cache: true
  freeze: true
  warning: false
  message: false
jupyter: python3
---
